### 2019-04-04 4-Listofpublications/Listofpublications.tex
Typo

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017, \href{https://hal.inria.fr/hal-02013847}{HAL-02013847}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, March 2017
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016, \href{https://hal.inria.fr/hal-02013839}{HAL-02013839}
\end{etaremune}

>>>>

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017, \href{https://hal.inria.fr/hal-02013847}{HAL-02013847}.
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, March 2017.
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016, \href{https://hal.inria.fr/hal-02013839}{HAL-02013839}.
\end{etaremune}
